\thesistitle

### 2019-08-18 sections/acknowledgements.tex
Vashisht

\chapter*{Acknowledgements}
Throughout the writing of this dissertation I have received a great deal of support and assistance. I would first like to thank my supervisor, Dr. A.M. Oprescu , whose expertise was invaluable in the academic writing and mathematical aspects of this thesis.

Next, I would like to thank my peer student Sander Meester for always being there when I was stuck. Whenever I needed to test some ideas you would always provide realistic insights. The long conversations about the problems I have been dealing with in my thesis would not have been solved in the same way if it wasn't for you. Your proofreading efforts helped take my writing to the next level.

>>>>

\chapter*{Acknowledgements}
Throughout the writing of this dissertation I have received a great deal of support and assistance. I would first like to thank my supervisor, Dr. A.M. Oprescu , whose expertise was invaluable in the academic writing and mathematical aspects of this thesis. I would like to thank you for your patience whilst reading my texts, as my words often required quite some editing to concisely deliver the message I try to deliver.

Next, we would like to thank my peer student Sander Meester for always being there when I was stuck. Whenever I needed to test some ideas you would always provide realistic insights. The long conversations about the problems I have been dealing with in my thesis would not have been solved in the same way if it wasn't for you. Your proofreading efforts helped take my writing to the next level.

I would like to thank my supervisor, Xander Schrijen, for all his input during our weekly meetings. We had long discussions about all my ideas, which helped to put my ideas in perspective.

I would like to thank Danny van Bruggen for all his help in my use of JavaParser. I am amazed by his willingness to help others to tackle their problems. JavaParser is at the core of the CloneRefactor tool and without Danny, I would never have come as far in the development of this tool.

### 2019-08-18 sections/related_work.tex
Vashisht

\section{Refactoring suggestion tools}
We are novel in the introduction of a fully automated refactoring tool. However, several tools have already been proposed for refactoring suggestion. In this section we discuss these tools. The tools are ordered on basis of the year in which they were proposed.

@@

@@

\subsection{Pattern‐based clone Refactoring Inspection (PRI)}
A study by Chen et al.~\ref{chen2018clone} addresses the problem that developers cannot easily determine which clones can be refactored or how they should be maintained scattered
throughout a large code base in evolving systems. They propose PRI, a technique for managing clone refactorings for clones with a Sibling relation. PRI is a plugin for the Eclipse IDE that shows which refactoring techniques can be used to refactor clones. Because it is integrated in the Eclipse IDE, the refactorings can be executed largely automatically, as this IDE has a large set of tools for performing such transformations.

PRI traces clones through revisions of a software project. This makes this tool able to find incompletely refactored clones. PRI produces false positives in that several groups are incorrectly classified since the clone detector suffers the inaccuracy in finding semantically equivalent behaviors between clones.

>>>>

\section{Code clone refactoring suggestion tools}
We are novel in the introduction of a fully automated refactoring tool. However, several tools have already been proposed for refactoring suggestion. In this section we discuss these tools. The tools are ordered on basis of the year in which they were proposed.

@@

\subsection{JDeodorant}
\todo{TODO}

@@

\subsection{Pattern‐based clone Refactoring Inspection (PRI)}
A study by Chen et al.~\ref{chen2018clone} addresses the problem that developers cannot easily determine which clones can be refactored or how they should be maintained scattered
throughout a large code base in evolving systems. They propose PRI, a technique for managing refactorings for clones with a Sibling relation. PRI is a plugin for the Eclipse IDE that shows which refactoring techniques can be used to refactor clones. Because it is integrated in the Eclipse IDE, the refactorings can be executed largely automatically, as this IDE has a large set of tools for performing such transformations.

Another feature of the PRI tool is to find incompletely refactored clones. To do this, PRI traces clones through revisions of a software project. When a clone class is incompletely refactored, PRI informs the user that there are clone instances for which an extracted method has already been created.

\section{Clone refatoring}
In this section, we shortly introduce recent studies about refactoring code clones.

\subsection{Impact of Clone Refactoring on External Quality Attributes}
A study by Vashisht et al.~\cite{vashisht2018impact} determines the impact of clone refactoring on several quality attributes. They calculate the metrics of the system before refactoring, detect clones using CCFinder \cite{kamiya2002ccfinder}, use JDeodorant to refactor a subset of the detected clones \cite{mazinanian2016jdeodorant} and measure the metrics again after refactoring to assess the impact of the refactoring process on quality attributes. They conclude that some metrics affect some quality attributes positively and some negatively.

In this study, the authors only compare before and after snapshots of refactoring the entire system. This makes it hard to determine why some metrics are negatively influenced.
